\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[english,a4paper,oneside]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Generating Higher-Order Coupling Functions for N-Body Oscillator Interations: A Python Library},
            colorlinks=true,
            linkcolor=blue,
            filecolor=Maroon,
            citecolor=Blue,
            urlcolor=Blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Fix footnotes in tables (requires footnote package)
\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{longtable}}{}
% Make links footnotes instead of hotlinks:
\DeclareRobustCommand{\href}[2]{#2\footnote{\url{#1}}}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi

\title{Generating Higher-Order Coupling Functions for N-Body Oscillator
Interations: A Python Library}
\author{true \and true}
\date{}

\begin{document}
\maketitle
\begin{abstract}
We document the nBodyCoupling library. The framework is reasonably
general, with no a priori restrictions on model dimension or type of
coupling function.
\end{abstract}

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

nBodyCoupling is a script for computing the higher-order coupling
functions in my paper with Dan Wilson, ``High-Order Accuracy Compuation
of Coupling Functions for Strongly Coupled Oscillators''. The script
generates higher-order interaction functions for phase reductions of
systems containing limit cycle oscillations.

\hypertarget{dependencies}{%
\subsection{Dependencies}\label{dependencies}}

All following libraries are required to make the script run.

\begin{longtable}[]{@{}lll@{}}
\toprule
Package & Version & Link\tabularnewline
\midrule
\endhead
Python & 3.8.1 &\tabularnewline
Matplotlib & 3.7.2 &\tabularnewline
Numpy & 1.21.6 &\tabularnewline
Scipy & 1.10.1 &\tabularnewline
Pathos & 0.2.8 & https://anaconda.org/conda-forge/pathos\tabularnewline
tqdm & 4.30.0 & https://anaconda.org/conda-forge/tqdm\tabularnewline
Sympy & 1.12 & https://anaconda.org/anaconda/sympy\tabularnewline
\bottomrule
\end{longtable}

Notes on depedendencies:

\textbf{Python 3.7+ is necessary}. Our code often requires an arbitrary
number of function inputs, which earlier versions of Python do not
allow. The script will likely work with earlier versions of all other
libraries.

\hypertarget{other-notes}{%
\subsubsection{Other Notes}\label{other-notes}}

Make sure to use \textbf{pathos} over multiprocessing because pickling
is more robust with pathos. Pathos uses dill, which can serialize far
more objects compared to multiprocessing, which uses pickle.

The code is written so that tqdm is necessary, but tqdm only provides a
status bar during parallel computing. It is not part of the engine, and
the code can be modified to work without it. In future versions I may
leave tqdm as a toggle.

\hypertarget{installation}{%
\subsection{Installation}\label{installation}}

As long as your computer has the packages listed above and they are
installed using Python 3.7, the nBodyCoupling script should run. Just
place it within the same working directory as your Python script and
import it as a module.

I have no immediate plans to release the nBodyCoupling script as an
installable package simply because I do not have the time to maintain
and track version releases for distribution platforms such as anaconda,
pip, and apt.

\hypertarget{reproduce-figures}{%
\section{Reproduce Figures}\label{reproduce-figures}}

To reproduce the figures in Park and Wilson 2020, cd to the examples
directory and run

\$ generate\_figures.py

This file will call the complex Ginzburg-Landau (CGL) model file
(CGL.py) and the thalamic model file (Thalamic.py) and generate the
figures from the paper. I've taken care of most of the work and made
sure that the code uses saved data files for figure generation as
opposed to computing everything from scratch. If you don't have the data
files, it will take a while to run, and will use 8 cores by default.
Make sure to edit the keyword arguments (documented in the nBodyCoupling
section below) if you wish to use more or less cores.

\hypertarget{nBodyCoupling}{%
\section{\texorpdfstring{Module
\texttt{nBodyCoupling}}{Module nBodyCoupling}}\label{nBodyCoupling}}

StrongCoupling.py computes the higher-order interaction functions from
Park and Wilson 2020 for \(N=2\) models and one Floquet multiplier. In
broad strokes, this library computes functions in the following order:

\begin{itemize}
\tightlist
\item
  Use the equation for \(\Delta x\) (15) to produce a hierarchy of ODEs
  for \(g^{(k)}\) and solve. (Wilson 2020)
\item
  Do the same using (30) and (40) to generate a hierarchy of ODEs for
  \(Z^{(k)}\) and \(I^{(k)}\), respectively. (Wilson 2020)
\item
  Solve for \(\phi\) in terms of \(\theta_i\), (13), (14) (Park and
  Wilson 2020)
\item
  Compute the higher-order interaction functions (15) (Park and Wilson
  2020)
\end{itemize}

Assumptions: -homogeneous vector fields -NO SELF COUPLING

Notes: - pA requires endpoint=False. make sure corresponding dxAs are
used.

\hypertarget{functions}{%
\subsection{Functions}\label{functions}}

\hypertarget{nBodyCoupling.augment_axes}{%
\subsubsection{\texorpdfstring{Function
\texttt{augment\_axes}}{Function augment\_axes}}\label{nBodyCoupling.augment_axes}}

\begin{quote}
\begin{verbatim}
def augment_axes(
    a,
    dims,
    repeat=True
)
\end{verbatim}
\end{quote}

fill a with repeat elements in new axes. new axes are in dims. set
repeat=True for function values set repeat=False for Fourier.

\hypertarget{nBodyCoupling.collect_nsep}{%
\subsubsection{\texorpdfstring{Function
\texttt{collect\_nsep}}{Function collect\_nsep}}\label{nBodyCoupling.collect_nsep}}

\begin{quote}
\begin{verbatim}
def collect_nsep(
    var_list,
    fn_list
)
\end{verbatim}
\end{quote}

extract the sep and nsep

\hypertarget{nBodyCoupling.equal_ignore_order}{%
\subsubsection{\texorpdfstring{Function
\texttt{equal\_ignore\_order}}{Function equal\_ignore\_order}}\label{nBodyCoupling.equal_ignore_order}}

\begin{quote}
\begin{verbatim}
def equal_ignore_order(
    a,
    b
)
\end{verbatim}
\end{quote}

Use only when elements are neither hashable nor sortable!

\hypertarget{nBodyCoupling.flatten}{%
\subsubsection{\texorpdfstring{Function
\texttt{flatten}}{Function flatten}}\label{nBodyCoupling.flatten}}

\begin{quote}
\begin{verbatim}
def flatten(
    xs
)
\end{verbatim}
\end{quote}

\hypertarget{nBodyCoupling.get_slice_dim}{%
\subsubsection{\texorpdfstring{Function
\texttt{get\_slice\_dim}}{Function get\_slice\_dim}}\label{nBodyCoupling.get_slice_dim}}

\begin{quote}
\begin{verbatim}
def get_slice_dim(
    n,
    dims
)
\end{verbatim}
\end{quote}

n: dimension of h function dims: dimensions to update with coefficients

\hypertarget{nBodyCoupling.module_exists}{%
\subsubsection{\texorpdfstring{Function
\texttt{module\_exists}}{Function module\_exists}}\label{nBodyCoupling.module_exists}}

\begin{quote}
\begin{verbatim}
def module_exists(
    module_name
)
\end{verbatim}
\end{quote}

\hypertarget{nBodyCoupling.unique_v_f1}{%
\subsubsection{\texorpdfstring{Function
\texttt{unique\_v\_f1}}{Function unique\_v\_f1}}\label{nBodyCoupling.unique_v_f1}}

\begin{quote}
\begin{verbatim}
def unique_v_f1(
    vars_list,
    fns_list
)
\end{verbatim}
\end{quote}

\hypertarget{nBodyCoupling.unique_vf}{%
\subsubsection{\texorpdfstring{Function
\texttt{unique\_vf}}{Function unique\_vf}}\label{nBodyCoupling.unique_vf}}

\begin{quote}
\begin{verbatim}
def unique_vf(
    var_list,
    fn_list
)
\end{verbatim}
\end{quote}

\hypertarget{nBodyCoupling.varcount}{%
\subsubsection{\texorpdfstring{Function
\texttt{varcount}}{Function varcount}}\label{nBodyCoupling.varcount}}

\begin{quote}
\begin{verbatim}
def varcount(
    var_list
)
\end{verbatim}
\end{quote}

get unique vars in var\_list

\hypertarget{nBodyCoupling.varcount_min}{%
\subsubsection{\texorpdfstring{Function
\texttt{varcount\_min}}{Function varcount\_min}}\label{nBodyCoupling.varcount_min}}

\begin{quote}
\begin{verbatim}
def varcount_min(
    var_list
)
\end{verbatim}
\end{quote}

count (not necessarily unique) vars in lists within var\_list

\hypertarget{classes}{%
\subsection{Classes}\label{classes}}

\hypertarget{nBodyCoupling.nBodyCoupling}{%
\subsubsection{\texorpdfstring{Class
\texttt{nBodyCoupling}}{Class nBodyCoupling}}\label{nBodyCoupling.nBodyCoupling}}

\begin{quote}
\begin{verbatim}
class nBodyCoupling(
    rhs,
    coupling,
    LC_init,
    var_names,
    pardict,
    **kwargs
)
\end{verbatim}
\end{quote}

See the defaults dict below for allowed kwargs.

All model parameters must follow the convention `parameter\_val'. No
other underscores should be used. the script splits the parameter name
at '\_' and uses the string to the left as the sympy parmeter name.

Reserved names: \ldots{}

\begin{verbatim}
rhs: callable.
    right-hand side of a model
coupling: callable.
    coupling function between oscillators
LC_init: list or numpy array.
    initial condition of limit cycle (must be found manually).
    XPP is useful, otherwise integrate your RHS for various
    initial conditions for long times and extract an initial
    condition close to the limit cycle.

LC_long_sim_time: float or int.
    Simulation time to compute the trjactory of an initial 
    condition near the limit cycle solution. Used to
    estimate limit cycle initial condition for use 
    in the Newton method. Default: 500
LC_eps_time: float.
    Approximation of the time error estimate in Newton's
    method, e.g., (difference between initial conditions)/
    (LC_eps_time). Default: 1e-4
LC_tol: float:
    Error tolerance to stop Newton's method when computing
    the limit cycle. Default: 1e-13

var_names: list.
    list of variable names as strings
pardict: dict.
    dictionary of parameter values. dict['par1_val'] = float.
    Make sure to use par_val format, where each parameter name is
    followed by _val.
recompute_LC: bool.
    If True, recompute limit cycle. If false, load limit cycle if
    limit cycle data exists. Otherwise, compute. Default: False.

recompute_monodromy: bool.
    If true, recompute kappa, the FLoquet multiplier using the
    monodromy matrix. If false, load kappa if data exists,
    otherwise compute. Default: False.
recompute_g_sym: bool.
    If true, recompute the symbolic equations for g^k. If false,
    load the symbolic equations if they exist in storage.
    Otherwise, compute. Default: False.
recompute_g: bool.
    If true, recompute the ODEs for g^k. If false,
    load the data for g^k if they exist in storage.
    Otherwise, compute. Default: False.

recompute_het_sym: bool.
    If true, recompute the symbolic equations for z^k and i^k.
    If false, load the symbolic equations if they exist in
    storage. Otherwise, compute. Default: False.
recompute_z: bool.
    If true, recompute the ODEs for z^k. If false,
    load the data for z^k if they exist in storage.
    Otherwise, compute. Default: False.
recompute_i: bool.
    If true, recompute the ODEs for i^k. If false,
    load the data for i^k if they exist in storage.
    Otherwise, compute. Default: False.

recompute_k_sym: bool.
    If true, recompute the symbolic equations for K^k. If false,
    load the symbolic equations if they exist in storage.
    Otherwise, compute. Default: False.
recompute_p_sym: bool.
    If true, recompute the symbolic equations for p^k. If false,
    load the symbolic equations if they exist in storage.
    Otherwise, compute. Default: False.
recompute_k_sym: bool.
    If true, recompute the symbolic equations for H^k. If false,
    load the symbolic equations if they exist in storage.
    Otherwise, compute. Default: False.

recompute_gij: bool
    recompute the pairwise functions for the psi expansions

recompute_h: bool.
    If true, recompute the H functions for H^k. If false,
    load the data equations if they exist in storage.
    Otherwise, compute. Default: False.
g_forward: list or bool.
    If bool, integrate forwards or backwards
    when computing g^k. If list, integrate g^k forwards or
    backwards based on bool value g_forward[k].
    Default: False.
z_forward: list or bool.
    Same idea as g_forward for PRCS. Default: False.

i_forward: list or bool.
    Same idea as g_forward for IRCS. Default: False.
dense: bool.
    If True, solve_ivp uses dense=True and evaluate solution
    along tLC.
dir: str.
    Location of data directory. Please choose carefully
    because some outputs may be on the order of gigabytes
    if NA >= 5000. Write 'home+data_dir/' to save to the folder
    'data_dir' in the home directory. Otherwise the script
    will use the current working directory by default uless
    an absolute path is used. The trailing '/' is
    required. Default: None.

trunc_order: int.
    Highest order to truncate the expansion. For example, 
    trunc_order = 3 means the code will compute up to and 
    including order 3. Default: 3.
NA: int.
    Number of partitions to discretize phase when computing p.
    Default: 500.
p_iter: int.
    Number of periods to integrate when computing the time 
    interal in p. Default: 10.

max_iter: int.
    Number of Newton iterations. Default: 20.
TN: int.
    Total time steps when computing g, z, i.
rtol, atol: float.
    Relative and absolute tolerance for ODE solvers.
    Defaults: 1e-7, 1e-7.

rel_tol: float.
    Threshold for use in Newton scheme. Default: 1e-6.
method: string.
    Specify the method used in scipy.integrate.solve_ivp.
    Default: LSODA.
g_bad_dx: list or bool. If bool, use another variable to increase
    the magnitude of the Newton derivative. This can only be
    determined after attempting to run simulations and seeing that
    the Jacobian for the Newton step is ill-conditioned. If list,
    check for ill-conditioning for each order k.
    For example, we use g_small_dx = [False,True,False,...,False]
    for the thalamic model. The CGL model only needs
    g_small_idx = False

z_bad_idx: same idea as g_small_idx for PRCs
i_bad_idx: same idea as g_small_idx for IRCs

N: total number of oscillators
coupling_mat: function, coupling matrix. shape
    must equal N, i.e., coupling_mat().shape[i] == N
    for i = 0, 1.
\end{verbatim}

\hypertarget{methods}{%
\paragraph{Methods}\label{methods}}

\hypertarget{nBodyCoupling.nBodyCoupling.fLam_ij}{%
\subparagraph{\texorpdfstring{Method
\texttt{fLam\_ij}}{Method fLam\_ij}}\label{nBodyCoupling.nBodyCoupling.fLam_ij}}

\begin{quote}
\begin{verbatim}
def fLam_ij(
    self,
    fn,
    i,
    j
)
\end{verbatim}
\end{quote}

interp2db object

\hypertarget{nBodyCoupling.nBodyCoupling.fmod}{%
\subparagraph{\texorpdfstring{Method
\texttt{fmod}}{Method fmod}}\label{nBodyCoupling.nBodyCoupling.fmod}}

\begin{quote}
\begin{verbatim}
def fmod(
    self,
    fn
)
\end{verbatim}
\end{quote}

fn has mod built-in

input function-like. usually interp1d object

needed to keep lambda input variable unique to fn.

otherwise lambda will use the same input variable for all lambda
functions.

\hypertarget{nBodyCoupling.nBodyCoupling.generate_g}{%
\subparagraph{\texorpdfstring{Method
\texttt{generate\_g}}{Method generate\_g}}\label{nBodyCoupling.nBodyCoupling.generate_g}}

\begin{quote}
\begin{verbatim}
def generate_g(
    self,
    k,
    het_vec
)
\end{verbatim}
\end{quote}

generate Floquet eigenfunctions g

uses Newtons method

\hypertarget{nBodyCoupling.nBodyCoupling.generate_gij}{%
\subparagraph{\texorpdfstring{Method
\texttt{generate\_gij}}{Method generate\_gij}}\label{nBodyCoupling.nBodyCoupling.generate_gij}}

\begin{quote}
\begin{verbatim}
def generate_gij(
    self
)
\end{verbatim}
\end{quote}

calculate convolution terms g\_\{ij\} for oscillator i and order k.

\hypertarget{nBodyCoupling.nBodyCoupling.generate_h_brute}{%
\subparagraph{\texorpdfstring{Method
\texttt{generate\_h\_brute}}{Method generate\_h\_brute}}\label{nBodyCoupling.nBodyCoupling.generate_h_brute}}

\begin{quote}
\begin{verbatim}
def generate_h_brute(
    self,
    i,
    k,
    idxarr1,
    idxarr2
)
\end{verbatim}
\end{quote}

use this if nyquist frequency is too high brute force + parallelization
across CPU cores.

\hypertarget{nBodyCoupling.nBodyCoupling.generate_h_fourier}{%
\subparagraph{\texorpdfstring{Method
\texttt{generate\_h\_fourier}}{Method generate\_h\_fourier}}\label{nBodyCoupling.nBodyCoupling.generate_h_fourier}}

\begin{quote}
\begin{verbatim}
def generate_h_fourier(
    self,
    i,
    k
)
\end{verbatim}
\end{quote}

\hypertarget{nBodyCoupling.nBodyCoupling.generate_het_sym}{%
\subparagraph{\texorpdfstring{Method
\texttt{generate\_het\_sym}}{Method generate\_het\_sym}}\label{nBodyCoupling.nBodyCoupling.generate_het_sym}}

\begin{quote}
\begin{verbatim}
def generate_het_sym(
    self
)
\end{verbatim}
\end{quote}

Generate heterogeneous terms for integrating the Z\_i and I\_i terms.

Returns

None.

\hypertarget{nBodyCoupling.nBodyCoupling.generate_i}{%
\subparagraph{\texorpdfstring{Method
\texttt{generate\_i}}{Method generate\_i}}\label{nBodyCoupling.nBodyCoupling.generate_i}}

\begin{quote}
\begin{verbatim}
def generate_i(
    self,
    k,
    het_vec
)
\end{verbatim}
\end{quote}

i0 equation is stable in forwards time i1, i2, etc equations are stable
in backwards time.

\hypertarget{nBodyCoupling.nBodyCoupling.generate_k_sym}{%
\subparagraph{\texorpdfstring{Method
\texttt{generate\_k\_sym}}{Method generate\_k\_sym}}\label{nBodyCoupling.nBodyCoupling.generate_k_sym}}

\begin{quote}
\begin{verbatim}
def generate_k_sym(
    self
)
\end{verbatim}
\end{quote}

generate terms involving the coupling term (see K in paper).

\hypertarget{nBodyCoupling.nBodyCoupling.generate_limit_cycle}{%
\subparagraph{\texorpdfstring{Method
\texttt{generate\_limit\_cycle}}{Method generate\_limit\_cycle}}\label{nBodyCoupling.nBodyCoupling.generate_limit_cycle}}

\begin{quote}
\begin{verbatim}
def generate_limit_cycle(
    self
)
\end{verbatim}
\end{quote}

\hypertarget{nBodyCoupling.nBodyCoupling.generate_z}{%
\subparagraph{\texorpdfstring{Method
\texttt{generate\_z}}{Method generate\_z}}\label{nBodyCoupling.nBodyCoupling.generate_z}}

\begin{quote}
\begin{verbatim}
def generate_z(
    self,
    k,
    het_vec
)
\end{verbatim}
\end{quote}

\hypertarget{nBodyCoupling.nBodyCoupling.get_index}{%
\subparagraph{\texorpdfstring{Method
\texttt{get\_index}}{Method get\_index}}\label{nBodyCoupling.nBodyCoupling.get_index}}

\begin{quote}
\begin{verbatim}
def get_index(
    self,
    fn
)
\end{verbatim}
\end{quote}

fn: sympy variable either x0 or p0{[}0{]}

returns (0,) or (0,0), respectively.

\hypertarget{nBodyCoupling.nBodyCoupling.interp_lam}{%
\subparagraph{\texorpdfstring{Method
\texttt{interp\_lam}}{Method interp\_lam}}\label{nBodyCoupling.nBodyCoupling.interp_lam}}

\begin{quote}
\begin{verbatim}
def interp_lam(
    self,
    k,
    fn_dict,
    fn_type='z'
)
\end{verbatim}
\end{quote}

it is too slow to call individual interpolated functions in the symbolic
heterogeneous terms. since the heterogeneous terms only depend on t,
just make and interpolated version and use that instead so only 1
function is called for the het. terms per iteration in numerical
iteration.

\hypertarget{nBodyCoupling.nBodyCoupling.load_g}{%
\subparagraph{\texorpdfstring{Method
\texttt{load\_g}}{Method load\_g}}\label{nBodyCoupling.nBodyCoupling.load_g}}

\begin{quote}
\begin{verbatim}
def load_g(
    self
)
\end{verbatim}
\end{quote}

load all Floquet eigenfunctions g or recompute

\hypertarget{nBodyCoupling.nBodyCoupling.load_g_sym}{%
\subparagraph{\texorpdfstring{Method
\texttt{load\_g\_sym}}{Method load\_g\_sym}}\label{nBodyCoupling.nBodyCoupling.load_g_sym}}

\begin{quote}
\begin{verbatim}
def load_g_sym(
    self
)
\end{verbatim}
\end{quote}

\hypertarget{nBodyCoupling.nBodyCoupling.load_gij}{%
\subparagraph{\texorpdfstring{Method
\texttt{load\_gij}}{Method load\_gij}}\label{nBodyCoupling.nBodyCoupling.load_gij}}

\begin{quote}
\begin{verbatim}
def load_gij(
    self
)
\end{verbatim}
\end{quote}

load or (re)calculate gij after implementing in p\_sym

\hypertarget{nBodyCoupling.nBodyCoupling.load_h}{%
\subparagraph{\texorpdfstring{Method
\texttt{load\_h}}{Method load\_h}}\label{nBodyCoupling.nBodyCoupling.load_h}}

\begin{quote}
\begin{verbatim}
def load_h(
    self
)
\end{verbatim}
\end{quote}

\hypertarget{nBodyCoupling.nBodyCoupling.load_h_sym}{%
\subparagraph{\texorpdfstring{Method
\texttt{load\_h\_sym}}{Method load\_h\_sym}}\label{nBodyCoupling.nBodyCoupling.load_h_sym}}

\begin{quote}
\begin{verbatim}
def load_h_sym(
    self
)
\end{verbatim}
\end{quote}

also compute h lam

\hypertarget{nBodyCoupling.nBodyCoupling.load_het_sym}{%
\subparagraph{\texorpdfstring{Method
\texttt{load\_het\_sym}}{Method load\_het\_sym}}\label{nBodyCoupling.nBodyCoupling.load_het_sym}}

\begin{quote}
\begin{verbatim}
def load_het_sym(
    self
)
\end{verbatim}
\end{quote}

\hypertarget{nBodyCoupling.nBodyCoupling.load_i}{%
\subparagraph{\texorpdfstring{Method
\texttt{load\_i}}{Method load\_i}}\label{nBodyCoupling.nBodyCoupling.load_i}}

\begin{quote}
\begin{verbatim}
def load_i(
    self
)
\end{verbatim}
\end{quote}

load all IRCs i or recomptue

\hypertarget{nBodyCoupling.nBodyCoupling.load_k_sym}{%
\subparagraph{\texorpdfstring{Method
\texttt{load\_k\_sym}}{Method load\_k\_sym}}\label{nBodyCoupling.nBodyCoupling.load_k_sym}}

\begin{quote}
\begin{verbatim}
def load_k_sym(
    self
)
\end{verbatim}
\end{quote}

k{[}i{]}{[}`type\_'+key{]}{[}j{]}{[}k{]} oscillator i, function type,
oscillator j, order k, variable name `key'.

c contains the derivatives of the coupling fn given oscillators i,j and
variable name `key'. c{[}i{]}{[}key{]}{[}j{]} same as k just without
terms collected.

\hypertarget{nBodyCoupling.nBodyCoupling.load_limit_cycle}{%
\subparagraph{\texorpdfstring{Method
\texttt{load\_limit\_cycle}}{Method load\_limit\_cycle}}\label{nBodyCoupling.nBodyCoupling.load_limit_cycle}}

\begin{quote}
\begin{verbatim}
def load_limit_cycle(
    self
)
\end{verbatim}
\end{quote}

\hypertarget{nBodyCoupling.nBodyCoupling.load_monodromy}{%
\subparagraph{\texorpdfstring{Method
\texttt{load\_monodromy}}{Method load\_monodromy}}\label{nBodyCoupling.nBodyCoupling.load_monodromy}}

\begin{quote}
\begin{verbatim}
def load_monodromy(
    self
)
\end{verbatim}
\end{quote}

if monodromy data exists, load. if DNE or recompute required, compute
here.

\hypertarget{nBodyCoupling.nBodyCoupling.load_p}{%
\subparagraph{\texorpdfstring{Method
\texttt{load\_p}}{Method load\_p}}\label{nBodyCoupling.nBodyCoupling.load_p}}

\begin{quote}
\begin{verbatim}
def load_p(
    self
)
\end{verbatim}
\end{quote}

insert lower order p{[}i{]} into higher order terms

\hypertarget{nBodyCoupling.nBodyCoupling.load_p_sym}{%
\subparagraph{\texorpdfstring{Method
\texttt{load\_p\_sym}}{Method load\_p\_sym}}\label{nBodyCoupling.nBodyCoupling.load_p_sym}}

\begin{quote}
\begin{verbatim}
def load_p_sym(
    self
)
\end{verbatim}
\end{quote}

generate/load the het. terms for psi ODEs.

to be solved using integrating factor meothod.\\
p{[}i{]}{[}`sym'{]}{[}k{]} is the forcing function for oscillator i of
order k

\hypertarget{nBodyCoupling.nBodyCoupling.load_z}{%
\subparagraph{\texorpdfstring{Method
\texttt{load\_z}}{Method load\_z}}\label{nBodyCoupling.nBodyCoupling.load_z}}

\begin{quote}
\begin{verbatim}
def load_z(
    self
)
\end{verbatim}
\end{quote}

load all PRCs z or recompute

\hypertarget{nBodyCoupling.nBodyCoupling.monodromy}{%
\subparagraph{\texorpdfstring{Method
\texttt{monodromy}}{Method monodromy}}\label{nBodyCoupling.nBodyCoupling.monodromy}}

\begin{quote}
\begin{verbatim}
def monodromy(
    self,
    t,
    z
)
\end{verbatim}
\end{quote}

calculate right-hand side of system

\(\dot \Phi = J\Phi, \Phi(0)=I\),

where \(\Phi\) is a matrix solution

jacLC is the jacobian evaluated along the limit cycle

\hypertarget{nBodyCoupling.nBodyCoupling.numerical_jac}{%
\subparagraph{\texorpdfstring{Method
\texttt{numerical\_jac}}{Method numerical\_jac}}\label{nBodyCoupling.nBodyCoupling.numerical_jac}}

\begin{quote}
\begin{verbatim}
def numerical_jac(
    self,
    fn,
    x,
    eps=1e-07
)
\end{verbatim}
\end{quote}

return numerical Jacobian function

\hypertarget{nBodyCoupling.nBodyCoupling.save_temp_figure}{%
\subparagraph{\texorpdfstring{Method
\texttt{save\_temp\_figure}}{Method save\_temp\_figure}}\label{nBodyCoupling.nBodyCoupling.save_temp_figure}}

\begin{quote}
\begin{verbatim}
def save_temp_figure(
    self,
    data,
    k,
    fn='plot',
    path_loc='figs_temp/'
)
\end{verbatim}
\end{quote}

data should be (TN,dim)

\hypertarget{Thalamic}{%
\section{\texorpdfstring{Module
\texttt{Thalamic}}{Module Thalamic}}\label{Thalamic}}

Example: Thalamic model from Wilson and Ermentrout RSTA 2019, Rubin and
Terman JCNS 2004

\hypertarget{functions-1}{%
\subsection{Functions}\label{functions-1}}

\hypertarget{Thalamic.coupling}{%
\subsubsection{\texorpdfstring{Function
\texttt{coupling}}{Function coupling}}\label{Thalamic.coupling}}

\begin{quote}
\begin{verbatim}
def coupling(
    vars_pair,
    pdict,
    option='val'
)
\end{verbatim}
\end{quote}

Synaptic coupling function between Thalamic oscillators.

E.g.,this Python function is the function \(G(x_i,x_j)\) in the equation
\(\frac{dx_i}{dt} = F(x_i) + \varepsilon G(x_i,x_j)\)

Parameters

\begin{verbatim}
vars_pair : list or array
    contains state variables from oscillator A and B, e.g.,
    vA, hA, rA, wA, vB, hB, rB, wB  
pdict : dict of flots or sympy objects.
    parameter dictionary pdict[key], val. key is always a string
    of the parameter. val is either the parameter value (float) or 
    the symbolic version of the parameter key.
option : string.
    Set to 'val' when inputs, t, z, pdict are floats. Set to
    'sym' when inputs t, z, pdict are sympy objects. The default
    is 'val'.
\end{verbatim}

Returns

\begin{verbatim}
numpy array or sympy Matrix
    returns numpy array if option == 'val'. 
    returns sympy Matrix if option == 'sym'
\end{verbatim}

\hypertarget{Thalamic.coupling_mat}{%
\subsubsection{\texorpdfstring{Function
\texttt{coupling\_mat}}{Function coupling\_mat}}\label{Thalamic.coupling_mat}}

\begin{quote}
\begin{verbatim}
def coupling_mat(
    N,
    option='val'
)
\end{verbatim}
\end{quote}

define coupling matrix.

\hypertarget{Thalamic.eval_lam_arr}{%
\subsubsection{\texorpdfstring{Function
\texttt{eval\_lam\_arr}}{Function eval\_lam\_arr}}\label{Thalamic.eval_lam_arr}}

\begin{quote}
\begin{verbatim}
def eval_lam_arr(
    pts,
    lam=None
)
\end{verbatim}
\end{quote}

use this for vectorizing lamban until i figure out something better

\hypertarget{Thalamic.main}{%
\subsubsection{\texorpdfstring{Function
\texttt{main}}{Function main}}\label{Thalamic.main}}

\begin{quote}
\begin{verbatim}
def main()
\end{verbatim}
\end{quote}

\hypertarget{Thalamic.rhs}{%
\subsubsection{\texorpdfstring{Function
\texttt{rhs}}{Function rhs}}\label{Thalamic.rhs}}

\begin{quote}
\begin{verbatim}
def rhs(
    t,
    z,
    pdict,
    option='val'
)
\end{verbatim}
\end{quote}

Right-hand side of the Thalamic model from Wilson and Ermentrout RSTA
2019 and Rubin and Terman JCNS 2004

Parameters

\begin{verbatim}
t : float or sympy object.
    time
z : array or list of floats or sympy objects.
    state variables of the thalamic model v, h, r, w.
pdict : dict of flots or sympy objects.
    parameter dictionary pdict[key], val. key is always a string
    of the parameter. val is either the parameter value (float) or 
    the symbolic version of the parameter key.
option : string.
    Set to 'val' when inputs, t, z, pdict are floats. Set to
    'sym' when inputs t, z, pdict are sympy objects. The default
    is 'val'.
\end{verbatim}

Returns

\begin{verbatim}
numpy array or sympy Matrix
    returns numpy array if option == 'val'
    returns sympy Matrix if option == 'sym'
\end{verbatim}

\hypertarget{CGL}{%
\section{\texorpdfstring{Module \texttt{CGL}}{Module CGL}}\label{CGL}}

Example: Complex Ginzburgh-Landau (CGL) model from Wilson and Ermentrout
RSTA 2019

\hypertarget{functions-2}{%
\subsection{Functions}\label{functions-2}}

\hypertarget{CGL.cgl3}{%
\subsubsection{\texorpdfstring{Function
\texttt{cgl3}}{Function cgl3}}\label{CGL.cgl3}}

\begin{quote}
\begin{verbatim}
def cgl3(
    t,
    y,
    pdict,
    eps
)
\end{verbatim}
\end{quote}

assume y has 8 coordinates. (x1,y1),(x2,y2),(x3,y3),(x4,y4)

\hypertarget{CGL.cgl4}{%
\subsubsection{\texorpdfstring{Function
\texttt{cgl4}}{Function cgl4}}\label{CGL.cgl4}}

\begin{quote}
\begin{verbatim}
def cgl4(
    t,
    y,
    pdict,
    eps
)
\end{verbatim}
\end{quote}

assume y has 8 coordinates. (x1,y1),(x2,y2),(x3,y3),(x4,y4)

\hypertarget{CGL.coupling}{%
\subsubsection{\texorpdfstring{Function
\texttt{coupling}}{Function coupling}}\label{CGL.coupling}}

\begin{quote}
\begin{verbatim}
def coupling(
    vars_pair,
    pdict,
    option='value'
)
\end{verbatim}
\end{quote}

Diffusive coupling function between Complex Ginzburgh Landau (CGL)
oscillators.

E.g.,this Python function is the function \(G(x_i,x_j)\) in the equation
\(\frac{dx_i}{dt} = F(x_i) + \varepsilon \sum_{j=1}^N G(x_i,x_j)\)

Parameters

\begin{verbatim}
vars_pair : list or array
    contains state variables from oscillator A and B, e.g.,
    x1,y1,x2,y2
pdict : dict of flots or sympy objects.
    parameter dictionary pdict[key], val. key is always a string
    of the parameter. val is either the parameter value (float) or 
    the symbolic version of the parameter key.
option : string.
    Set to 'val' when inputs, t, z, pdict are floats. Set to
    'sym' when inputs t, z, pdict are sympy objects. The default
    is 'val'.
\end{verbatim}

Returns

\begin{verbatim}
* numpy array or sympy Matrix
    * returns numpy array if option == 'val'. 
    returns sympy Matrix if option == 'sym'
\end{verbatim}

\hypertarget{CGL.coupling_mat}{%
\subsubsection{\texorpdfstring{Function
\texttt{coupling\_mat}}{Function coupling\_mat}}\label{CGL.coupling_mat}}

\begin{quote}
\begin{verbatim}
def coupling_mat(
    N,
    option='val'
)
\end{verbatim}
\end{quote}

define coupling matrix.

\hypertarget{CGL.d_estimate}{%
\subsubsection{\texorpdfstring{Function
\texttt{d\_estimate}}{Function d\_estimate}}\label{CGL.d_estimate}}

\begin{quote}
\begin{verbatim}
def d_estimate(
    a,
    eps,
    dx=1e-05
)
\end{verbatim}
\end{quote}

estimate derivate of function of 4 vars a: object

\hypertarget{CGL.h_at_0}{%
\subsubsection{\texorpdfstring{Function
\texttt{h\_at\_0}}{Function h\_at\_0}}\label{CGL.h_at_0}}

\begin{quote}
\begin{verbatim}
def h_at_0(
    a,
    eps
)
\end{verbatim}
\end{quote}

\hypertarget{CGL.main}{%
\subsubsection{\texorpdfstring{Function
\texttt{main}}{Function main}}\label{CGL.main}}

\begin{quote}
\begin{verbatim}
def main()
\end{verbatim}
\end{quote}

\hypertarget{CGL.phase_o1_th}{%
\subsubsection{\texorpdfstring{Function
\texttt{phase\_o1\_th}}{Function phase\_o1\_th}}\label{CGL.phase_o1_th}}

\begin{quote}
\begin{verbatim}
def phase_o1_th(
    t,
    y,
    o,
    eps
)
\end{verbatim}
\end{quote}

phase theta (as opposed to phase diffs phi) right-hand side of phase
equations t: time y: phase diff variables o: object

\hypertarget{CGL.phase_o2_th}{%
\subsubsection{\texorpdfstring{Function
\texttt{phase\_o2\_th}}{Function phase\_o2\_th}}\label{CGL.phase_o2_th}}

\begin{quote}
\begin{verbatim}
def phase_o2_th(
    t,
    y,
    o,
    eps
)
\end{verbatim}
\end{quote}

2nd lowest order phase theta (as opposed to phase diffs phi) right-hand
side of phase equations t: time y: phase diff variables o: object

\hypertarget{CGL.phase_o3_th}{%
\subsubsection{\texorpdfstring{Function
\texttt{phase\_o3\_th}}{Function phase\_o3\_th}}\label{CGL.phase_o3_th}}

\begin{quote}
\begin{verbatim}
def phase_o3_th(
    t,
    y,
    o,
    eps
)
\end{verbatim}
\end{quote}

2nd lowest order phase theta (as opposed to phase diffs phi) right-hand
side of phase equations t: time y: phase diff variables o: object

\hypertarget{CGL.phase_phi}{%
\subsubsection{\texorpdfstring{Function
\texttt{phase\_phi}}{Function phase\_phi}}\label{CGL.phase_phi}}

\begin{quote}
\begin{verbatim}
def phase_phi(
    t,
    y,
    o,
    eps
)
\end{verbatim}
\end{quote}

right-hand side of phase equations t: time y: phase diff variables o:
object

\hypertarget{CGL.rhs}{%
\subsubsection{\texorpdfstring{Function
\texttt{rhs}}{Function rhs}}\label{CGL.rhs}}

\begin{quote}
\begin{verbatim}
def rhs(
    t,
    z,
    pdict,
    option='value'
)
\end{verbatim}
\end{quote}

Right-hand side of the Complex Ginzburgh-Landau (CGL) model from Wilson
and Ermentrout RSTA 2019

Parameters

\begin{verbatim}
t : float or sympy object.
    time
z : array or list of floats or sympy objects.
    state variables of the thalamic model v, h, r, w.
pdict : dict of flots or sympy objects.
    parameter dictionary pdict[key], val. key is always a string
    of the parameter. val is either the parameter value (float) or 
    the symbolic version of the parameter key.
option : string.
    Set to 'val' when inputs, t, z, pdict are floats. Set to
    'sym' when inputs t, z, pdict are sympy objects. The default
    is 'val'.
\end{verbatim}

Returns

\begin{verbatim}
numpy array or sympy Matrix
    returns numpy array if option == 'val'
    returns sympy Matrix if option == 'sym'
\end{verbatim}

Generated by \emph{pdoc} 0.10.0 (\url{https://pdoc3.github.io}).

\end{document}
